Pillar 1 - Sequential Pattern Mining

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
knit results

    item_taken= paste(item, taken, sep = "_")

@@

We generate sequence rules:
```{r SR taken, cache = TRUE}
#Generating sequence rules:
SR_taken   <- my_SR(data = sequences   )
```

```{r SR PF, cache = TRUE}
##pass/fail filter
SR_PF      <- my_SR(data = sequences_PF) %>% 
  filter(str_detect(rhs,"fail"))
```

```{r SR HL, cache = TRUE}
##high/low filter
SR_HL      <- my_SR(data = sequences_HL)%>% 
  filter(str_detect(rhs,"low"))
```

```{r SR grade, cache = TRUE}
SR_Grade   <- my_SR(data = sequences_Grade )
```

```{r SR grade exp, cache = TRUE}
#Grades filter 
SR_expanded_Grade   <- my_SR(data = sequences_expanded_Grade )
```

>>>>

    item_taken= paste(item, taken, sep = "_"),
    item_taken_grade= case_when(
      is.na(Grade) ~ paste(item, taken, sep = "_"),
      T            ~ paste(item, PF)
    )

@@

We generate sequence rules:
```{r SR taken, cache = TRUE}

#Generating sequence rules:
SR_taken   <- my_SR(data = sequences   )
```

```{r SR PF, cache = TRUE}

##pass/fail filter
SR_PF      <- my_SR(data = sequences_PF) %>% 
  filter(str_detect(rhs,"fail"))
```

```{r SR HL, cache = TRUE}

##high/low filter
SR_HL      <- my_SR(data = sequences_HL)%>% 
  filter(str_detect(rhs,"low"))
```

```{r SR grade, cache = TRUE}

SR_Grade   <- my_SR(data = sequences_Grade )
```

```{r SR grade exp, cache = TRUE}

#Grades filter 
SR_expanded_Grade   <- my_SR(data = sequences_expanded_Grade )
```
